On Misuses of the Kolmogorov--Smirnov Test for One-Sample Goodness-of-Fit

### 2022-11-14 manuscript/manuscript.tex
minor
smoothed early section 3

The Kolmogorov-Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized parametric distribution.
Let $X_1, ..., X_n$ be a random sample of size~$n$ from a continuous
distribution. The null hypothesis $H_0$ is that $X_i$'s follow distribution~$F$.
Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function. The KS test statistic is
\begin{equation}
  \label{eq:ks_standard}
  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}
The asymptotic distribution of $D_n$ under $H_0$ is independent of the
distribution~$F$. As $n \to \infty$, $D_n$ converges in distribution to
the supremum of standard Brownian bridge \citep{kolmogorov1933sulla}. For large
samples, the tests can be performed with a table \citep{smirnov1948table}.
Critical values for small samples ($n \le 35$) has also been given
\citep{Massey}. The KS test is available in popular
statistical software packages, such as function \texttt{ks.test} in R package
\textsf{stats} \citep{R, Marsaglia}.

The standard one-sample KS test applies to independent data with a continuous
hypothesized distribution that is completely specified. In practice, however, it
has often been applied without realizing that one or more of these assumptions
do not hold. For example, \citet{Noether} demonstrated the conservativeness of
the KS test when applied to discontinuous distributions. The null distribution
of the KS statistic is no longer distribution free. Computing the
exact and asymptotic distribution of $D_n$ is challenging. Fortunately, the null
distribution of the KS statistic when the underlying distribution is
discontinuous has been efficiently addressed by \citet{Dimitrova} with an
companion R package \textsf{KSgeneral}. Although a common misuse of KS test, the
issue with discontinuous or data is not our focus.

When the hypothesized distribution contains fitted parameters, as is the case in
most goodness-of-fit test settings, the standard KS test is not applicable.
\citet{Steinskog} ``discovers'' the change in power
when using fitted parameters and stresses caution in using the KS test in
such ways. In fact, using fitted parameters in place of the true parameters in
KS test is long known to yield extremely conservative results
\citep[e.g.,][]{Lilliefors}. This problem can be solved by parametric
bootstrap \citep{efron1985bootstrap, hall1991two}, where
bootstrap samples of the testing statistics are constructed from samples
generated from the fitted hypothesized distribution. A nonparametric bootstrap
solution is not trivial because the a nonparametric bootstrap sample of the
observed data have ties, which would not happen for continuous distributions.
\citet{Babu} derived the bias of standard nonparametric bootstrap and
showed how to correct it. They further noted that both parametric and
non-parametric procedures lead to correct asymptotic levels.

The standard KS test does not apply to serially dependent data either. The
distribution of the KS statistic would have a higher variance for positively
dependent data than that derived when the data are independent because of a
smaller effective sample size. For example, for
testing normality, \citet{Durilleul} demonstrates that a naive application of
the KS statistic is too liberal for medium-to-high positive serieal dependence,
and that for negative dependence, the behavior is asymmetrical. For remedies,
\citet{Weiss} provides a procedure that is applicable specifically for data
modeled by the second-order auto-regressive (AR) process where the AR parameters
are known. \citet{Lanzante} tests various strategies for dealing with temporal
dependence and concludes that a test based on Monte-Carlo simulations performed
the best. When additionally the hypothesized distribution contains unknown
parameters, the standard KS test becomes even further inapplicable.

@@

The null hypothesis of a goodness-of-fit test is often a composite hypothesis
instead of a single hypothesis. That is, the hypothesized distribution is a
family of distributions with unspecified parameters instead of a specific member
in this family. Let $F_\theta$ be a family of distributions indexed by parameter
vector~$\theta$. The null hypothesis is
\[
  H_0: \text{the random sample $X_1, \ldots, X_n$
    comes from a distribution $F_\theta$ with some $\theta$.}
\]
Since $\theta$ is unknown, one would naturally estimate $\theta$ by
$\hat\theta_n$ from, for example, maximum likelihood or methods of moments. The
KS statistic would then be computed as
\begin{equation}
  \label{eq:ks_fitted}
  D_n = \sqrt{n} \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
\end{equation}
An overly large $D_n$ still indicates evidence to reject~$H_0$. To get the
p-value of the observed $D_n$, however, the null distribution is not the same as
that in the standard
case~\eqref{eq:ks_standard}. If the same null distribution were used, one would
be testing a different~$H_0$ that the random sample comes from the specific
member distribution~$F_{\hat\theta}$ instead of the family~$F_\theta$.

@@

Nonparametric bootstrap can also be used to approximate the null distribution
of the testing statistic with the bias correction from \citet{Babu}:
\begin{enumerate}
\item
  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
  with replacement
\item
  Fit $F_\theta$ to the sample and obtain estimate $\hat\theta_n^*$ of $\theta$.
\item
  Obtain the empirical distribution function of the random sample $F_n^*$
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) - B_n(x) |.
  \]
  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
  bias term \citep{Babu}
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $D^*$ to approximate the null distribution of the observed
  statistic.
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
are greater than or equal to~$D_n$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_fitted}
  \caption{The Naive plot (left) is the histogram of p-values from the standard
  KS test with fitted parameters. The Parametric plot (middle) is the histogram
  of p-values from implementing parametric bootstrap. The Babu plot (right) is
  the histogram of p-values from implementing nonparametric bootstrap with a
  correction for bias. In each case, $1000$ replicate tests were performed on
  the standard normal distribution with sample size $n = 100$. $B = 1000$
  bootstrap samples are obtained for each test. \eds{perhaps use density hist vs
	freq. hist (here and elsewhere)?}}
  \label{fig:hist_fitted}
\end{figure}

@@

The KS test also displays issues in the case of dependent data. As mentioned, an
assumption of the test is that the data is independent. Real data, however,
is often temporally or spatially dependent and the results of a goodness-of-fit
test would be valuable. When the KS test is performed on dependent data it
performs poorly. In this situation, the null hypothesis is $H_0$: the random
sample $X_1, \ldots, X_n$ come from a continuous distribution $F$ where $F$ has
completely specified parameters. The test statistic is the same as
Equation~\eqref{eq:ks_standard}. However, since the data is dependent, the null
hypothesis is wrong and must be corrected.
\eds{null hypothesis or null distribution? or both?}
This is demonstrated with a
simulation in Figure~\ref{fig:hist_correlation}. Data is generated from a
first-order autoregressive model (AR(1)) with a standard normal distribution.
P-values are gathered from $1000$ replicate tests for different levels of the
AR coefficient $\psi$, varying from $(-3,3)$.
\eds{how are these p-values calculated?}
In the presence of serially
dependent data, the distribution of p-values no longer follows $U(0, 1)$ as
would be expected of a valid test. The results echo those of \citet{Durilleul}
that the KS statistic is too liberal in the presence of positive
autocorrelation, and that the behavior is asymmetrical for negative
 autocorrelation.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_correlation}
  \caption{Each histogram is a plot of the p-values of standard KS tests
  performed on dependent data simulated from an AR(1) process of the standard
  normal distribution. The titles represent the various levels of the AR
  coefficient $\psi$ tested. The sample size is $n = 100$ and $1000$ replicate
  tests were performed for each AR coefficient.}
  \label{fig:hist_correlation}
\end{figure}

In order to correct this, we can employ a parametric bootstrap procedure which
assumes a working serial dependence structure through copulas. A copula is a
multivariate distribution with standard uniform marginal distributions, which
completely characterizes the dependence structure of a multivariate
distribution \citep{Copula, Hofert}. For simplicity, we assume a normal copula
with an AR(1) structure to characterize the serial dependence of the
observations. The AR(1) parameter $r$ of the normal copula is set to match the
sample serial Spearman's rho of the observed data.
\eds{What is the difference between $\psi$ and $r$?}
The procedure is as
follows.

\begin{enumerate}
\item
  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
  coefficient $r$ such that the $Z_i$'s are $N(0, 1)$ variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$, where $\Phi$ is the
  distribution function of $N(0, 1)$, $i = 1, \ldots, n$, whose first-order
  sample Spearman's rho matches that of the observed data.
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
    distribution of the $B$ test statistics to approximate
    the null distribution of the observed statistic.
\end{enumerate}

Throughout the simulation we assume a working AR(1) dependence structure
regardless of the true dependence. If the true dependence is indeed a normal
copula with an AR(1) structure, this method is exact. When the true dependence
is not AR(1), it may still give a reasonable approximation that can be useful
for practical purposes. This is demonstrated with different dependence
structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.

@@

The procedure demonstrated in Section~\ref{sec:dependence} works when the data
is dependent and the hypothesized distribution is completely specified. However,
this is not practical. In practice we do not know the parameters of the
hypothesized distribution. Therefore, it is valuable to have a procedure that
corrects for both fitted parameters and serially dependent data. The remedy
using copulas can be modified to be effective in the case where both assumptions
must be violated. The null hypothesis is equivalent to Section~\ref{sec:fitted}
and the test statistic is equal to Equation~\eqref{eq:ks_fitted}. The bootstrap
procedure in Section~\ref{sec:fitted} is no longer valid because the serial
dependence is not accounted for. Let $r$ be the AR(1) coefficient of the normal
copula that matches the sample first-order Spearman's rho of the observed data
as obtained by the \texttt{iRho} function in the \textsf{copula} package
\citep{Copula}. We propose the following bootstrap procedure to assess the
significance of the observed KS statistic.

@@

The KS test has base assumptions that the hypothesized distribution is
completely specified and the data is independent. When these assumptions are
violated, the test is no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and non-parametric bootstrap can restore
the size of the test. A bias correction is required if the non-parametric form
is used \citep{Babu}. In the case of \eds{serially} dependent data, a procedure
using bootstrap
with copulas to model dependency shows positive results. When both assumptions
are violated, i.e., where the data has \eds{serial} dependence and parameters
must
be fitted, an adjusted copula procedure also shows positive results. The tests
appear effective for a variety of families of distributions. The copula remedy
is not a complete solution and has limitations. Regardless of the true
dependence, we assume an AR(1) dependence structure. Therefore, if the AR(1)
dependence structure is a close approximation of the truth, the approach can work.
However, in cases such as AR(2), if the approximation is too far from the true
dependence structure the approach does not completely remedy the issue. As well,
tests were only performed with the normal copula. It is possible that other
copulas could provide stronger results based on the true dependence of the data.

>>>>

The Kolmogorov-Smirnov (KS) test is one of the most popular goodness-of-fit
tests for comparing a sample with a hypothesized parametric distribution.
Let $X_1, ..., X_n$ be a random sample of size~$n$ from a continuous
distribution. The null hypothesis $H_0$ is that $X_i$'s follow distribution~$F$.
Let $F_n(t) = \sum_{i=1}^n I(X_i \le t) / n$ be the empirical cumulative
distribution function of the sample, where $I(\cdot)$ is the indicator
function. The KS test statistic is
\begin{equation}
  \label{eq:ks_standard}
  D_n = \sqrt{n} \sup_x | F_{n}(x) - F(x) |.
\end{equation}
The asymptotic distribution of $D_n$ under $H_0$ is independent of the
distribution~$F$. As $n \to \infty$, $D_n$ converges in distribution to
the supremum of standard Brownian bridge \citep{kolmogorov1933sulla}. For large
samples, the tests can be performed with a table \citep{smirnov1948table}.
Critical values for small samples ($n \le 35$) has also been given
\citep{massey1951kolmogorov}. The KS test is available in popular
statistical software packages, such as function \texttt{ks.test} in R package
\textsf{stats} \citep{R, marsaglia2003evaluating}.

The standard one-sample KS test applies to independent data with a continuous
hypothesized distribution that is completely specified. In practice, however, it
has often been applied without realizing that one or more of these assumptions
do not hold. For example, \citet{noether1963note} showed the conservativeness of
the KS test when applied to discontinuous distributions. The null distribution
of the KS statistic is no longer distribution free. Computing the
exact and asymptotic distribution of $D_n$ is challenging. Fortunately, the null
distribution of the KS statistic for discontinuous distributions has been
efficiently addressed by \citet{dimitrova2020computing} with an
companion R package \textsf{KSgeneral}. Although a common misuse of KS test, the
issue with discontinuous or data is not our focus.

When the hypothesized distribution~$F$ contains unspecified parameters, as is
the case in most goodness-of-fit test settings, the standard KS test is not
applicable. \citet{steinskog2007cautionary} ``discovers'' the change in power
when using fitted parameters and stresses caution in using the KS test in
such ways. In fact, using fitted parameters in place of the true parameters in
KS test is long known to yield extremely conservative results
\citep[e.g.,][]{lilliefors1967kolmogorov}. This problem can be solved by
parametric bootstrap \citep{efron1985bootstrap, hall1991two}, where
bootstrap samples of the testing statistics are constructed from samples
generated from the fitted hypothesized distribution. A nonparametric bootstrap
solution is not trivial because the a nonparametric bootstrap sample of the
observed data have ties, which would not happen for continuous distributions.
\citet{babu2004goodness} derived the bias of standard nonparametric bootstrap and
showed how to correct it. They further noted that both parametric and
non-parametric procedures lead to correct asymptotic levels.

The standard KS test does not apply to stationary yet dependent data either. The
distribution of the KS statistic would have a higher variance for positively
dependent data than that derived when the data are independent because of a
smaller effective sample size. For example, for testing normality,
\citet{durilleul1992lack} demonstrates that a naive application of
the KS statistic is too liberal for medium-to-high positive serieal dependence,
and that for negative dependence, the behavior is asymmetrical. For remedies,
\citet{weiss1978modification} provides a procedure that is applicable specifically for data
modeled by the second-order auto-regressive (AR) process where the AR parameters
are known. \citet{lanzante2021testing} tests various strategies for dealing with temporal
dependence and concludes that a test based on Monte-Carlo simulations performed
the best. When additionally the hypothesized distribution contains unknown
parameters, the standard KS test becomes even further inapplicable.

@@

The null hypothesis of a goodness-of-fit test is often a composite hypothesis
instead of a single hypothesis. That is, the hypothesized distribution is a
family of distributions with unspecified parameters instead of a specific member
in this family. Let $F_\theta$ be a family of distributions indexed by parameter
vector~$\theta$. The null hypothesis is
\[
  H_0: \text{the random sample $X_1, \ldots, X_n$
    comes from a distribution $F_\theta$ with some $\theta$.}
\]
Since $\theta$ is unknown, one would naturally estimate $\theta$ by
$\hat\theta_n$ from, for example, maximum likelihood or methods of moments. The
KS statistic would then be computed as
\begin{equation}
  \label{eq:ks_fitted}
  D_n = \sqrt{n} \sup_x | F_n(x) - F_{\hat\theta_n}(x) |.
\end{equation}
An overly large $D_n$ still indicates evidence to reject~$H_0$. To get the
p-value of the observed $D_n$, however, note that the null distribution is not
the same as that in the standard
case~\eqref{eq:ks_standard}. If the same null distribution were used, one would
be testing a different~$H_0$ that the random sample comes from the specific
member distribution~$F_{\hat\theta}$ instead of the family~$F_\theta$.

@@

Nonparametric bootstrap can also be used to approximate the null distribution
of the testing statistic with the bias correction from \citet{babu2004goodness}:
\begin{enumerate}
\item
  Draw a random sample $X_1^*,...,X_n^*$ from the empirical distribution $F_n$
  with replacement
\item
  Fit $F_\theta$ to the sample and obtain estimate $\hat\theta_n^*$ of $\theta$.
\item
  Obtain the empirical distribution function of the random sample $F_n^*$
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x | F_n^* (x)- F_{\hat\theta_n}^*(x) - B_n(x) |.
  \]
  where $B_{n}(x) = \sqrt{n}(F_{n}(x) - F_{\hat\theta_n}(x))$ is the known
  bias term \citep{babu2004goodness}
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of $D^*$ to approximate the null distribution of the observed
  statistic.
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
are greater than or equal to~$D_n$.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_fitted}
  \caption{Histograms of p-values for the KS test with unspecified parameters in
    the hypothesized distribution based on 1000 replicates of sample size
    $n = 100$. Naive (left): KS test with KS statistic calculated based on fitted
    parameters. Parametric bootstrap (center): KS test with parametric
    bootstrap. Nonparametric bootstrap (right): KS test with nonparametric
    bootstrap using the bias correction from \citet{babu2004goodness}.
    \eds{perhaps use density hist vs
	freq. hist (here and elsewhere)?}}
  \label{fig:hist_fitted}
\end{figure}

@@

When the observed data $X_1, \ldots, X_n$ are not independent but serially
dependent, the null distribution of the KS statistic $D_n$
in~\eqref{eq:ks_standard} changes. For a
stationary series, it may still be of interest to test whether the data come
from a completely specified distribution~$F$. When the serial dependence is
positive, the effective sample size is less than~$n$. The testing statistic
would be stochastically greater than that obtained from independent data, making
it more likely to reject the null hypothesis than it should. So the test is
liberal. The reasoning is similar when the serial dependence is negative,
in which case, the test is conservative.

The invalidity of the statndard statistic for serially dependent data can be
illustrated by a simple simulation study. Consider a first-order autoregressive
or AR(1) model with marginal standard normal distribution. For each AR
coefficient $\psi \in \{-0.3, 0.2, 0.1, 0, 0.1, 0.2, 0.3\}$, we generated 1000
series of length 100. For each series, we applied the KS statistic
in~\eqref{eq:ks_standard} to test $H_0$ that the $X_i$'s follow $N(0, 1)$
marginally. The histograms of the p-values from $1000$ replicates for all the
$\psi$ values are displayed in Figure~\ref{fig:hist_correlation}. When
$\phi \ne 0$, the histograms do not look like to be generated from a standard
uniform distribution. Positive $\psi$ values led to liberal p-values while
negative $\psi$ values led to conservative p-values. The larger the magnitude of
$\psi$, the bigger the deviation from the desired level.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{hist_correlation}
  \caption{Histograms of p-values for the KS test applied to data generated from
    AR(1) processes with AR coefficients
    $\psi \in \{-0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3\}$
    based on 1000 replicates of sample size $n = 100$.}
  \label{fig:hist_correlation}
\end{figure}

A complete remedy for the KS tests with serially dependent data is
challenging. The null distribution depends on the structure of the serial
dependence, which can be arbitrary in practice. A parametric bootstrap procedure
would need model specification of the dependence, whereas the primary interest
is to test the marginal distribution of the stationary series. A block
nonparametric bootstrap for stationary data \citep{kunsch1989jackknife} is
attempting, but the counterpart of a bias correction as in
\citet{babu2004goodness} is not available yet. Is there any approach that does
not require fully specification of the dependence of the stationary process
but still gives reasonably satisfactory correction to the size of the KS test in
certain applications?

We propose a semiparametric bootstrap procedure that assumes a working serial
dependence structure which does not need to be correctly specified. The working
serial dependence is introduced through copulas with the hope to approximate the
true serial dependence as allowed by the working copulas. A copula is a
multivariate distribution with standard uniform marginal distributions, which
completely characterizes the dependence structure of a multivariate
distribution \citep{hofert2018elements}. It separates the dependence structure
of a multivariate distribution from its marginal distributions. The normal copula
is the copula determined by the multivariate normal distribution. We propose to
use a normal working copula with an AR(1) structure to approximate the serial
dependence of the observations. Let $\hat\rho$ be the lag-1 sample auto
Spearman's rho of the observed data. A normal copula of dimension~$n$ can be
constructed with an AR(1) structure and its AR coefficient~$\psi$ is chosen to
ensure that the Spearman's rho matches $\hat\rho$. Let $\psi(\hat\rho)$ denote
this coefficient. The bootstrap procedure is as follows.
\begin{enumerate}
\item
  Generate $Z_1, \ldots, Z_n$ from an AR(1) process with autocorrelation
  coefficient $\psi(\hat\rho)$ such that the $Z_i$'s are $N(0, 1)$ variables.
\item
  Form a bootstrap sample $X_i^* = F^{-1} [\Phi(Z_i)]$,  $i = 1, \ldots, n$,
  where $\Phi$ is the distribution function of $N(0, 1)$.
\item
  Obtain the empirical distribution function $F_n^*$ of the bootstrap sample
  $X_1^*, \ldots, X_n^*$.
\item
  Calculate bootstrap KS statistic
  \[
    D^* = \sup_x \lvert F_n^* (x)- F(x) \rvert.
  \]
\item
  Repeat the previous steps a large number $B$ times and use the empirical
  distribution of the $B$ test statistics to approximate
  the null distribution of the observed statistic.
\end{enumerate}
The p-value of $D_n$ is, again, approximated by the proportion of $D_n^*$'s that
are greater than or equal to~$D_n$.

This process is semiparametric because the marginal distribution is
parametrically specified while the dependence structure of the stationary series
is only approximated. The closer the approximation is to the truth, the better
performance of the size of the KS test  If the true dependence is indeed a
normal copula with an AR(1) structure, this method is exact. When the true
dependence is not AR(1), it may still give a reasonable approximation that can
be useful for practical purposes. More complicated working models other
than the AR(1) process could be used, but we focus here on the AR(1) model.

Continuing with the simulation study, 
Throughout the simulation we assume a working AR(1) dependence structure
regardless of the true dependence. This is demonstrated with different dependence
structures in Figure~\ref{fig:hist_ma1_arma_ar2_D}.

@@

The procedure demonstrated in Section~\ref{sec:dependence} works when the data
is dependent and the hypothesized distribution is completely specified. However,
this is not practical. In practice we do not know the parameters of the
hypothesized distribution. Therefore, it is valuable to have a procedure that
corrects for both fitted parameters and serially dependent data. The remedy
using copulas can be modified to be effective in the case where both assumptions
must be violated. The null hypothesis is equivalent to Section~\ref{sec:fitted}
and the test statistic is equal to Equation~\eqref{eq:ks_fitted}. The bootstrap
procedure in Section~\ref{sec:fitted} is no longer valid because the serial
dependence is not accounted for. Let $r$ be the AR(1) coefficient of the normal
copula that matches the sample first-order Spearman's rho of the observed data
as obtained by the \texttt{iRho} function in the \textsf{copula} package
\citep{Rpkg:copula}. We propose the following bootstrap procedure to assess the
significance of the observed KS statistic.

@@

The KS test has base assumptions that the hypothesized distribution is
completely specified and the data is independent. When these assumptions are
violated, the test is no longer accurate and remedies must be performed. In the
case of fitted parameters, parametric and non-parametric bootstrap can restore
the size of the test. A bias correction is required if the non-parametric form
is used \citep{babu2004goodness}. In the case of \eds{serially} dependent data, a procedure
using bootstrap
with copulas to model dependency shows positive results. When both assumptions
are violated, i.e., where the data has \eds{serial} dependence and parameters
must
be fitted, an adjusted copula procedure also shows positive results. The tests
appear effective for a variety of families of distributions. The copula remedy
is not a complete solution and has limitations. Regardless of the true
dependence, we assume an AR(1) dependence structure. Therefore, if the AR(1)
dependence structure is a close approximation of the truth, the approach can work.
However, in cases such as AR(2), if the approximation is too far from the true
dependence structure the approach does not completely remedy the issue. As well,
tests were only performed with the normal copula. It is possible that other
copulas could provide stronger results based on the true dependence of the data.
